### 2023-01-26 code/plots.Rmd
datafreeze: modified code/*.py files to create data in a standardized form. created final data files data/*.xz, removed previous data/*.gz files (still probably need to remove them from history with git filter-branch (TBD). Modified code blocks within manuscript.rmd to fit the new data form, things are stable here.
filename

```{r}
msy <- read_csv("../data/msy.csv.xz")
best <- best_reward(msy)
```

@@

```{r}
ppo <- read_csv("../data/PPO250.csv.gz")
```
```{r}
ppo_sim <- ppo |> 
  mutate(escapement = (X+1) - action * (X+1),
         effort = action) |>
  pivot_longer(c("X", "Y", "Z"),
               names_to = "species", values_to = "abundance") |>
  mutate(abundance = abundance + 1)
```

>>>>

```{r}
msy <- read_csv("../data/msy.csv.xz")
best <- best_reward(msy)
best
```

@@

```{r}
ppo <- read_csv("../data/PPO200.csv.xz")
```
```{r}
ppo_sim <- ppo |> 
  mutate(escapement = (X+1) - action * (X+1),
         effort = action) |>
  pivot_longer(c("X", "Y", "Z"),
               names_to = "species", values_to = "abundance") |>
  mutate(abundance = abundance + 1)
```
